Democracy, Public Support, and Measurement Uncertainty

### 2021-04-29 paper/dcpo_demsupport.Rmd
landscape

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 11pt
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
---

@@

length(unique(claassen_replication$country))

ls_country <- unique(claassen_replication_input$data$country)
first_year <- min(claassen_replication_input$data$year)

@@

# Online Supplementary Materials {-}
# (APPENDIX) Appendix {-}
# Numeric Results for Replicating @Claassen2020a

@@

# Numeric Results for Replicating @Claassen2020b

@@

>>>>

date: "`r format(Sys.time(), '%B %d, %Y')`"
editor_options: 
  markdown: 
    wrap: sentence
tables: true # enable longtable and booktabs
citation_package: natbib
fontsize: 11pt
linestretch: 1.5 # double spacing using linestretch 1.5
bibliography: dcpo_demsupport.bib
# bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), ".bib$", recursive = TRUE))`}
# csl: https://raw.githubusercontent.com/citation-style-language/styles/master/american-political-science-association.csl
biblio-style: apsr
citecolor: black
linkcolor: black
endnote: no
header-includes:
      - \usepackage{array}
      - \usepackage{caption}
      - \usepackage{graphicx}
      - \usepackage{siunitx}
      - \usepackage{colortbl}
      - \usepackage{multirow}
      - \usepackage{hhline}
      - \usepackage{calc}
      - \usepackage{tabularx}
      - \usepackage{threeparttable}
      - \usepackage{wrapfig}
      - \usepackage{fullpage}
      - \usepackage{lscape} #better for printing, page displayed vertically, content in landscape mode, \usepackage{pdflscape} better for screen, page displayed horizontally, content in landscape mode
---

@@

# length(unique(claassen_replication$country))
# 
# ls_country <- unique(claassen_replication_input$data$country)
# first_year <- min(claassen_replication_input$data$year)

ls_country <- unique(claassen_replication$country)
first_year <- min(claassen_replication$year)

@@

# Online Supplementary Materials {-}
# (APPENDIX) Appendix {-}
# Numeric Results for Replicating Claassen 2020a

@@

# Numeric Results for Replicating Claassen 2020b

\begin{landscape}

@@

\end{landscape}
